How to \emph{not} write Virtual Machines for Dynamic Languages

### 2007-05-27 talk/dyla2007/dyla.tex
Define the abbreviation "VM".

We argue in this paper that one should not write interpreters for dynamic
languages manually but rather use meta-programming techniques and raise the
overall level at which they are implemented. We believe this to be
ultimately a better investment of efforts than the development of more and more advanced
general-purpose object oriented VMs.

>>>>

We argue in this paper that one should not write interpreters for dynamic
languages manually but rather use meta-programming techniques and raise the
overall level at which they are implemented. We believe this to be
ultimately a better investment of efforts than the development of more and more advanced
general-purpose object oriented virtual machines (VMs).
